Tesseroids: command-line tools for gravity field forward modeling in spherical coordinates

### 2014-03-28 manuscript.tex
Added formula by Grombein

>>>>

The gravitational potential of a tesseroid is

\begin{equation}
    V(r,\phi,\lambda) = G \rho
        \int\limits_{\lambda_1}^{\lambda_2}
        \int\limits_{\phi_1}^{\phi_2}
        \int\limits_{r_1}^{r_2}
        \frac{1}{\ell} \kappa  dr' d\phi' d\lambda'
\end{equation}

The gravitational attraction
can be calculated using the formula
\citep{Grombein2013}:

\begin{equation}
    g_{\alpha}(r,\phi,\lambda) = G \rho
        \int\limits_{\lambda_1}^{\lambda_2}
        \int\limits_{\phi_1}^{\phi_2}
        \int\limits_{r_1}^{r_2}
        \frac{\Delta_{\alpha}}{\ell^3} \kappa dr' d\phi' d\lambda'
        \ \ \ \alpha \in \{x,y,z\}
\end{equation}

The gravity gradients can be calculated
using the general formula
\citep{Grombein2013}:

\begin{multline}
    g_{\alpha\beta}(r,\phi,\lambda) = G \rho
        \int\limits_{\lambda_1}^{\lambda_2}
        \int\limits_{\phi_1}^{\phi_2}
        \int\limits_{r_1}^{r_2}
        I_{\alpha\beta}({r'}, {\phi'}, {\lambda'})
        dr' d\phi' d\lambda'
        \\
        \alpha,\beta \in \{x,y,z\}
\end{multline}

\begin{equation}
    I_{\alpha\beta}({r'}, {\phi'}, {\lambda'}) =
        \left(
            \frac{3\Delta_{\alpha} \Delta_{\beta}}{\ell^5} -
            \frac{\delta_{\alpha\beta}}{\ell^3}
        \right)
        \kappa \ \ \ \alpha,\beta \in \{x,y,z\}
\end{equation}

where $\rho$ is density,
$\{x, y, z\}$ correspond to the local coordinate system
of the computation point P,
$\delta_{\alpha\beta}$ is the Kronecker delta, and

\begin{eqnarray}
    \Delta_x &=& r' K_{\phi} \\
    \Delta_y &=& r' \cos \phi' \sin(\lambda' - \lambda) \\
    \Delta_z &=& r' \cos \psi - r\\
    \ell &=& \sqrt{r'^2 + r^2 - 2 r' r \cos \psi} \\
    \cos\psi &=& \sin\phi\sin\phi' + \cos\phi\cos\phi'
                 \cos(\lambda' - \lambda) \\
    K_{\phi} &=& \cos\phi\sin\phi' - \sin\phi\cos\phi'
                 \cos(\lambda' - \lambda)\\
    \kappa &=& {r'}^2 \cos \phi'
\end{eqnarray}

$\phi$ is latitude,
$\lambda$ is longitude, and
$r$ is radius.
